---
title: "00_Preparing Transcripts for LIWC Analysis"
author: "Leeann Comfort"
date: "May 01, 2018"
output: html_document
---

## Overview
 **Purpose**  
  - This file transforms the raw interview transcripts (Wave 1 only), stored as copies of the original .docx files, into .csv files  
 
 **Output**   
   - A series of .csv files to the folder in which transcripts are stored
 
 **Notes**  
 - The .csv output files are organized so that each question/response is one observation  
 - Neither the original nor the transformed files are saved to github; the raw data is restricted per IRB protocol (ID: 2015-04-7512)   
 - The `read_transcript` function does not save any of the interviewee identifiers, that information is saved only in the filename
 - After the files are created, the files must be uploaded & processed by LIWC2015 software (liwc.net)  
 - R/RStudio would intermittently fail to recognize the secure network drive; this version of code runs off local computer desktop as temporary work-around  

******************  

## Setup
```{r setup, warning=FALSE, results=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/leeann.comfort/Desktop/Data")

# textreadr is used to read in word files as transcripts in csv format, where each observation is a question/response (used in line 31) 
install.packages("textreadr", repos="http://cran.rstudio.com/")
library(textreadr)  
```

## File Transformation
```{r, warning=FALSE}
# Create a list of all the files we need to transform
files <- list.files(path="./WAVE 1 - Transcripts", pattern="*.docx", full.names=T, recursive=FALSE)

# Saves the path length (in case the files ever move)
pl <- nchar("C:/Users/leeann.comfort/Desktop/Data/WAVE 1 - Transcripts")

# Creates a function to transform, rename, and save the document
func <- function(x) {
  # Reads in the file, with each response in a separate line (the skip=1)
  t1 <- read_transcript(x, skip = 1) 
  
  # Generates a file name by stripping the path  & changing the extension
  name <- paste0(substr(x,pl,nchar(x)-5),".csv")  
  
  # writes the file to a csv using the previously generated file name (nothing stored in environment)
  write.csv(t1, file=name)  
  }

# Apply the function to each of files in the folder
invisible(lapply(files, func))

# Confirm files written correctly
# list.files(pattern="*.csv", full.names=T, recursive=FALSE) 
```

**Note:** The final `list.files` results are redacted from the github version because the filenames contain identifiable information