---
title: "02 Exploratory Analyses"
author: "Leeann Comfort"
date: "April 28, 2018"
output: html_document
---

```{r setup}
knitr::opts_knit$set(root.dir = "C:/Users/leeann.comfort/Desktop/Data")
rm(list=ls())
library(ggplot2)
library(gridExtra)
library(grid)
library(tidyr)
library(purrr)
library(dplyr)
library(reshape)
df <- read.csv("C:/Users/leeann.comfort/Desktop/Data/liwc_one_2018-05-01.csv")
df <- liwc_one
names(df)
```


## Comparing High & Low Performing ACOs
These sections create basic, non-publication-worthy visuals just for the purposing of assessing the data

### Main Summary Variables
Summary variables are separated from the other variables because they tend to distort the shared graph axes
```{r }
# Select only the 4 Summary variables and the interviewee identifiers, then ansorm data in long format (so that DVs can be used as a facet)
  df_summary <- df[,c("aco", "perf", "site", "workgroup_collapsed", "speakanon","Analytic", "Clout", "Authentic","Tone")] %>% 
                melt(id=c("aco", "perf", "site", "workgroup_collapsed", "speakanon"))
 
# Generate graphs for each variable
    ggplot(df_summary, aes(x=perf, y=value)) + geom_boxplot() + facet_wrap(~variable) + 
      ylab("Summary Measure Score") + 
      xlab("High/Low Performing")
    ggsave(filename = "HL_SummaryVars.png", device='png')
  
```

### Graphs for other (non-summary) Variables
```{r}
#Select everything BUT the 4 Summary variables 
# Words-Per-Sentence also not included because it's largely influenced by the transcriber
  df_nonsum <- df[, !names(df) %in% c("X", "WC", "Analytic", "Clout", "Authentic", "Tone", "WPS")] %>% 
               melt(id=c("aco", "perf", "site", "workgroup_collapsed", "speakanon"))

# Generate graphs for each variable  
# Note that ggsave specifies a large area so that all graphs appear together in a scroll-able file for exploratory viewing
  ggplot(df_nonsum, aes(x=perf, y=value)) + geom_boxplot() + facet_wrap(~variable) + ylab("Proportion of Words") + xlab("High/Low Performing")
  ggsave(filename = "HL_NonSummaryVars.png", width = 10, height = 20, dpi = 150, units = "in", device='png')
```


## Compare Interviewer v. Interviewee Data
These analyses were used to determine that the interviewer language was fairly different from the interviewee data (for the summary variables), and so should be removed from statistical analyses (to remove noise)
```{r}
#Created a version of the dataset where the speaker IDs were characters so that all the interviewees could be recoded as "respondent"
df_int <- df
df$speakanon <- as.character(df$speakanon)
df$speakanon[df$speakanon != "interviewer"] = "respondent"
```


### Main Summary Variables
As before, summary variables are separated from the other variables because they tend to distort the shared graph axes
```{r}
# Select only the 4 Summary variables and the interviewee identifiers, then ansorm data in long format (so that DVs can be used as a facet)
  df_int_summary <- df_int[,c("aco", "perf", "site", "workgroup_collapsed", "speakanon","Analytic", "Clout", "Authentic","Tone")] %>% 
                  melt(id=c("aco", "perf", "site", "workgroup_collapsed", "speakanon"))

# Generate graphs for each variable
  ggplot(df_int_summary, aes(x=speakanon, y=value)) + geom_boxplot() + facet_wrap(~variable) + 
    ylab("Summary Measure Score") + 
    xlab("Interviewers v. Respondents")
  
  ggsave(filename = "IR_Summary.png", width = 10, height = 20, dpi = 150, units = "in", device='png')

```

### Graphs for other (non-summary) Variables
```{r}
#Select everything BUT the 4 Summary variables 
# Words-Per-Sentence also not included because it's largely influenced by the transcriber
  df_int_nonsum <- df_int[, !names(df_int) %in% c("X", "WC", "Analytic", "Clout", "Authentic", "Tone", "WPS")] %>% 
                    melt(id=c("aco", "perf", "site", "workgroup_collapsed", "speakanon"))

# Generate graphs for each variable  
# Note that ggsave specifies a large area so that all graphs appear together in a scroll-able file for exploratory viewing
  ggplot(df_int_nonsum, aes(x=speakanon, y=value)) + geom_boxplot() + facet_wrap(~variable) +
    ylab("Proportion of Words") + 
    xlab("Interviewers v. Respondents")
  ggsave(filename = "IR_NonSummary.png", width = 10, height = 20, dpi = 150, units = "in", device='png')

```


## Compare Data By Site
```{r}
#Create a version of the dataset where the site is a factor
df_site <- df
df_site$site <- as.factor(df_site$site)

# Drop observations where site == 0 (2 management interviews, only in the high performing sites so not comparable to low performing sites)
df_site <- df_site[!(df_site$site==0),]  
```


### Main Summary Variables
As before, summary variables are separated from the other variables because they tend to distort the shared graph axes
```{r}
# Select only the 4 Summary variables and the interviewee identifiers, then ansorm data in long format (so that DVs can be used as a facet)
  df_site_summary <- df_site[,c("aco", "perf", "site", "workgroup_collapsed", "speakanon","Analytic", "Clout", "Authentic","Tone")] %>% 
                     melt(id=c("aco", "perf", "site", "workgroup_collapsed", "speakanon"))

#Generate graphs for each variable
  ggplot(df_site_summary, aes(x=site, y=value, color=perf)) + geom_boxplot() + facet_wrap(~variable) + 
    ylab("Summary Measure Score") + 
    xlab("Sites")
  
  
  ggsave(filename = "Site_Summary.png", width = 10, height = 20, dpi = 150, units = "in", device='png')

```

### Graphs for other (non-summary) Variables
```{r}
#Select everything BUT the 4 Summary variables 
# Words-Per-Sentence also not included because it's largely influenced by the transcriber
  df_site_nonsum <- df_site[, !names(df_site) %in% c("X", "WC", "Analytic", "Clout", "Authentic", "Tone", "WPS")] %>% 
                    melt(id=c("aco", "perf", "site", "workgroup_collapsed", "speakanon"))

# Generate graphs for each variable  
# Note that ggsave specifies a large area so that all graphs appear together in a scroll-able file for exploratory viewing
  ggplot(df_site_nonsum, aes(x=site, y=value, color=perf)) + geom_boxplot() + facet_wrap(~variable) +
    ylab("Proportion of Words") + 
    xlab("Sites")
  
  ggsave(filename = "Site_NonSummary.png", width = 20, height = 40, dpi = 150, units = "in", device='png')

```




## Compare Data By Role
```{r}
#Create a version of the dataset where the role is a factor
df_role <- df
df_role$role <- as.factor(df_role$workgroup_collapsed)
```


### Main Summary Variables
As before, summary variables are separated from the other variables because they tend to distort the shared graph axes
```{r}
# Select only the 4 Summary variables and the interviewee identifiers, then ansorm data in long format (so that DVs can be used as a facet)
  df_role_summary <- df_role[,c("aco", "perf", "site", "role", "speakanon","Analytic", "Clout", "Authentic","Tone")] %>% 
                      melt(id=c("aco", "perf", "site", "role", "speakanon"))


# Generate graphs for each variable
  ggplot(df_role_summary, aes(x=role, y=value, color=perf)) + geom_boxplot() + facet_wrap(~variable) + 
    ylab("Summary Measure Score") + 
    xlab("Roles")
  
  ggsave(filename = "Role_Summary.png", width = 10, height = 20, dpi = 150, units = "in", device='png')

```

### Graphs for other (non-summary) Variables
```{r}
#Select everything BUT the 4 Summary variables 
# Words-Per-Sentence also not included because it's largely influenced by the transcriber
  df_site_nonsum <- df_site[, !names(df_site) %in% c("X", "WC", "Analytic", "Clout", "Authentic", "Tone", "WPS")] %>% 
                    melt(id=c("aco", "perf", "site", "workgroup_collapsed", "speakanon"))

# Generate graphs for each variable  
# Note that ggsave specifies a large area so that all graphs appear together in a scroll-able file for exploratory viewing
  ggplot(df_site_nonsum, aes(x=site, y=value, color=perf)) + geom_boxplot() + facet_wrap(~variable) +
    ylab("Proportion of Words") + 
    xlab("Sites")
  
  ggsave(filename = "Site_NonSummary.png", width = 20, height = 40, dpi = 150, units = "in", device='png')

```


Maybe X-Y Plots of different elements within LIWC?


```{r}


xyplot(Clout~Authentic|as.factor(speakanon),data=df2, 
       type=c("p","g","r"), 
       col="dark blue", 
       col.line="black", 
       xlab="authentic", 
       ylab="clout")

```

